---
title: "HW 02 - Airbnb listings in Edinburgh"
author: "Jordan Sabol"
date: "9/15/2021"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
library(ggridges)
```

## Exercises

### Exercise 1

``` {r numrow}
nrow(edibnb)
````

### Exercise 2

View(edibnb)

### Exercise 3


```{r prices-neighbourhoods}
  ggplot(data= edibnb, mapping = aes(x=price)) +
    geom_histogram(binwidth= 75) +
    facet_wrap(~ neighbourhood) +
    labs(title="Airbnb Prices by Neighbourhood",
         x="Price",
         y="Frequency")

```

### Exercise 4


```{r top-5-median}
  edibnb %>% 
    group_by(neighbourhood)%>%
      summarise(Median=as.numeric(median(price, na.rm=TRUE)))%>%
        arrange(desc(Median))%>%
        slice(1:5)
  
    
      
      
    
  
```

```{r top-5-median-plot}

  edibnb%>%
    filter(neighbourhood %in% c("New Town", "Old Town", "West End", 
                                "Stockbridge", "Bruntsfield"))
    ggplot(data= edibnb, mapping=aes(x=price, y=neighbourhood))+
      geom_density_ridges(alpha=0.5,
                          color="red"
                          )

```

```{r top-5-median-summary-stats}
  edibnb %>%
    filter(neighbourhood %in% c("New Town", "Old Town", "West End", 
                                "Stockbridge", "Bruntsfield")) %>%
    group_by(neighbourhood) %>%
    summarise(Min= min(price, na.rm=TRUE), 
              Mean= mean(price,  na.rm=TRUE), 
              Median= median(price, na.rm = TRUE),
              StdDev= sd(price, na.rm = TRUE),
              IQR= IQR(price, na.rm= TRUE),
              Max= max(price, na.rm=TRUE))
    
```

Based on the visualization & summary statistics, the distribution of the data (listing prices in those 5 neighborhoods) has a right skew.

### Exercise 5

The visualization shows the frequency of the review scores rating by neighborhood. As seen in
the graphs, most ratings fall in the 90+ range.

```{r review-scores-rating}

ggplot(data= edibnb, aes(x = review_scores_rating, fill = neighbourhood)) +
  geom_histogram(binwidth = 20) +
    labs(
      x = "Review Scores Rating",
      y = "Frequency",
      title = "Review Scores By Neighborhood") +
    facet_wrap(~ neighbourhood, nrow = 4)

```
